Target Readability in Interpersonal Accuracy

### 2022-05-16 manuscript.Rmd
update the html

```{r message=FALSE, include=FALSE, results='hide'}
library(tidyverse)
library(lme4)
library(lmerTest)
```

@@

# import data for exploratory predictors
paths <- dir_ls(here("data"))
df_names <- gsub(".+data/(.+)\\.sav", "\\1", paths)

@@

# Make variable types/names congruent for merging
# rename
ind_diffs_self %<>% 
  rename(PerUn = SubNum)

@@

## Descriptive statistics for Empathic Accuracy
```{r}
descriptive_df <-
df %>% 
  select(
    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
    SIAS, SPS, SIAPS, Extr, Agree, Consc, Neurot, Open
  )

table1 <-
tibble(
  var = names(descriptive_df),
  mean = map_dbl(descriptive_df, mean, na.rm = TRUE),
  sd = map_dbl(descriptive_df, sd, na.rm = TRUE)
)
```
Table 1 represents descriptive statistics for all the variables in the present study.

@@

```{r}
# affect
samEACaggdata <- rio::import(here::here("data", "samdata.csv"))

@@

## extract empirical bayesian estimates for targets
EBTRTtar <- ranef(SAM1)$TarUn
colnames(EBTRTtar)<-c("Intercept","TSR","Norm")
EBTRTtar$TarUn<-as.numeric(row.names(EBTRTtar))
map_dbl(EBTRTtar, sd)

@@

## fit a model for each perceiver
models_dyad <- 
samdata %>% 
  group_by(PerUn) %>% 
  nest() %>% 
  mutate(models = map(data, ~ {

    lm(ptrait ~ targSRrC + AvgtraitC, 
              data = .x)

  }
                      )
         )
```

```{r}
# affect

>>>>

```{r message=FALSE, include=FALSE, results='hide'}
library(tidyverse)
library(lme4)
library(lmerTest)
library(rio)
```

@@

# import data for exploratory predictors
paths <- fs::dir_ls(here::here("data"))
df_names <- gsub(".+data/(.+)\\.sav", "\\1", paths)

@@

# Make variable types/names congruent for merging
# rename
library(magrittr)
ind_diffs_self %<>% 
  rename(PerUn = SubNum)

@@

## Descriptive statistics for Empathic Accuracy
```{r, include = FALSE}
descriptive_df <-
df %>% 
  select(
    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
    SIAS, SPS, SIAPS, Extr, Agree, Consc, Neurot, Open
  )

table1 <-
tibble(
  var = names(descriptive_df),
  mean = map_dbl(descriptive_df, mean, na.rm = TRUE),
  sd = map_dbl(descriptive_df, sd, na.rm = TRUE)
)
```

Table 1 represents descriptive statistics for all the variables in the present study.

@@

```{r}
# affect
samEACaggdata <- import(here::here("data", "c_affect.csv"))

samEAC_null <- lmer (Part ~ 1 + 
                  (1|PerUn) + 
                  (1|TarUn) + 
                  (1|DyUn), 
                data = samEACaggdata)

sjPlot::tab_model(samEAC_null)

@@

## extract empirical bayesian estimates for targets
EBTRTtar <- ranef(SAM1)$TarUn
EBTRTtar$TarUn<-as.numeric(row.names(EBTRTtar))
map_dbl(EBTRTtar, sd)

@@

## fit a model for each perceiver
# models_dyad <- 
# samdata %>% 
#   group_by(PerUn) %>% 
#   nest() %>% 
#   mutate(models = map(data, ~ {
#     
#     lm(ptrait ~ targSRrC + AvgtraitC, 
#               data = .x)
#     
#   }
#                       )
#          )
```

```{r}
# affect
samEAC <- lmer (Part ~ targSRrC + NormC + 
                  (targSRrC + NormC|PerUn) + 
                  (targSRrC + NormC|TarUn) + 
                  (targSRrC + NormC|DyUn), 
                data = samEACaggdata)

summary(samEAC)
